Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2018-01-26 TACAS2018/paper.tex
sec 6

In this section, we describe our technique for synthesizing safe
digital feedback controllers using CEGIS. Broadly speaking, CEGIS
denotes an iterative technique where each iteration performs inductive
generalisation based on counterexamples provided by a verification
engine. In each iteration, an inductive synthesiser produces a
candidate solution that obeys the specification for a limited number
of inputs. Subsequently, this candidate is passed to a verification
oracle that checks it against the specification for all possible
inputs. If the verification fails, then the witness counterexample is
passed back to the synthesis phase, where it is added to the set of
inputs to be considered in the next loop iteration. Otherwise, we are
done.

%
We enhance the standard CEGIS architecture with abstraction refinement
and optimization, resulting in CEGIS-OR (CEGIS with Optimization and
Refinement).  By using abstraction refinement, CEGIS-OR tackles the
scalability issues inherent in program synthesis as it allows using
potentially coarse abstractions of a system that are only refined on
demand.  Given that the use of coarse abstractions could result in low
quality candidate solutions (i.e. candidates that fail the
specification on a very large number of inputs), after each synthesis
phase we use optimization techniques to improve the produced
candidates.  In particular, our optimization procedure aims at
reducing the size of the reach space of the closed loop system while
maintaining other verification properties. \note{what are other
  verification properties?  if you mean safety and stability say so.}

@@

The benchmark suite employed to evaluate the proposed technique is 
composed by 7 SISO models extracted from the literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15,maglev,converters}.
In order to obtain statistically relevant results, we have taken these models
and modified each possible combination of their parameters by a 10\% tolerance,
thus creating seven hundred benchmarks from this base.
In the verification module, we have used the tool Axelerator~\cite{} .

>>>>

In this section, we describe our technique for synthesizing safe
digital feedback controllers using CEGIS \note{add ref}. Broadly speaking, CEGIS
denotes an iterative technique where each iteration performs inductive
generalisation based on counterexamples provided by a verification
engine. In each iteration, an inductive synthesiser produces a
candidate solution that obeys the specification for a limited number
of inputs. Subsequently, this candidate is passed to a verification
oracle that checks it against the specification for all possible
inputs. If the verification fails, then the witness counterexample is
passed back to the synthesis phase, where it is added to the set of
inputs to be considered in the next loop iteration. Otherwise, we are
done.

%
We enhance the standard CEGIS architecture with abstraction refinement
and optimization, resulting in CEGIS-OR (CEGIS with Optimization and
Refinement).  By using abstraction refinement, CEGIS-OR tackles the
scalability issues inherent in program synthesis as it allows using
potentially coarse abstractions of a system that are only refined on
demand.  Given that the use of coarse abstractions could result in low
quality candidate solutions (i.e. candidates that fail the
specification on a very large number of inputs), after each synthesis
phase we use optimization techniques to improve the produced
candidates.  In particular, our optimization procedure aims at
reducing the size of the reach space \note{define reach space} of the closed loop system while
maintaining other verification properties. \note{what are other
  verification properties?  if you mean safety and stability say so.}

@@

The benchmark suite employed to evaluate the proposed technique is 
composed by seven SISO \note{defined SISO} models extracted from the control literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15,maglev,converters}.
In order to obtain statistically relevant results, we have taken these models
and modified each possible combination of their parameters by a 10\% tolerance,
thus creating seven hundred benchmarks from this base.
In the verification module, we have used the tool Axelerator~\cite{} .
